Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-09-28 manuscript/usses_water_ms.Rmd
adds journal paper number
fixes small things for PeerJ submission

Community composition was similar among treatments.
The multidimensional space of community composition overlapped among treatments in all years and was equally dispersed in all years (Table 2; Fig. 5).
Community composition was also remarkably stable over time, with no evidence of divergence among treatments (Table 2; Fig. 5).

@@

The similarity of ecosystem functional response (Fig. 3) and community composition (Fig. 5) among treatments is surprising because grasslands generally, and sagebrush steppe specifically, are considered water-limited systems.
Indeed, we expected ecosystem functional response, community composition, or both to change under our treatments.
Why did our treatments fail to induce ecosystem or community responses?
We can think of three reasons; two are limitations of our study, and one is the life history traits of the species in our focal communities.
We first discuss the potential limitations of our study, and then discuss the biological explanation.

@@

In conclusion, our results suggest the species in our focal plant community are insensitive to to changes in precipitation regime. 
Such insensitivity can buffer species against precipitation variability in this semi-arid ecosystem, making them successful in the long run.
Longer, chronic precipitation alteration might reveal plant community shifts that we did not observe [e.g., @Wilcox2016]. 
For example, a long-term increase in water availability could allow species that do not bet hedge to gain prominence and dominate the ecosystem functional response.
Our results suggest compositional shifts would have the largest impact at high rainfall because the current community maintained consistent ecosystem functional response at very low water availability.

@@

This research was supported by the Utah Agricultural Experiment Station, Utah State University, and approved as journal paper number XXXX.
The research was also supported by the National Science Foundation, through a Postdoctoral Research Fellowship in Biology and Mathematics to ATT (DBI-1400370), a Graduate Research Fellowship to ARK, and grants DEB-1353078 and DEB-1054040 to PBA.

>>>>

Community composition was similar among treatments.
The multidimensional space of community composition overlapped among treatments in all years and was equally dispersed in all years (Table 2; Fig. 4).
Community composition was also remarkably stable over time, with no evidence of divergence among treatments (Table 2; Fig. 4).

@@

The similarity of ecosystem functional response (Fig. 3) and community composition (Fig. 4) among treatments is surprising because grasslands generally, and sagebrush steppe specifically, are considered water-limited systems.
Indeed, we expected ecosystem functional response, community composition, or both to change under our treatments.
Why did our treatments fail to induce ecosystem or community responses?
We can think of three reasons; two are limitations of our study, and one is the life history traits of the species in our focal communities.
We first discuss the potential limitations of our study, and then discuss the biological explanation.

@@

# CONCLUSIONS

Our results suggest the species in our focal plant community are insensitive to to changes in precipitation regime. 
Such insensitivity can buffer species against precipitation variability in this semi-arid ecosystem, making them successful in the long run.
Longer, chronic precipitation alteration might reveal plant community shifts that we did not observe [e.g., @Wilcox2016]. 
For example, a long-term increase in water availability could allow species that do not bet hedge to gain prominence and dominate the ecosystem functional response.
Our results suggest compositional shifts would have the largest impact at high rainfall because the current community maintained consistent ecosystem functional response at very low water availability.

@@

This research was supported by the Utah Agricultural Experiment Station, Utah State University, and approved as journal paper number 9035.
The research was also supported by the National Science Foundation, through a Postdoctoral Research Fellowship in Biology and Mathematics to ATT (DBI-1400370), a Graduate Research Fellowship to ARK, and grants DEB-1353078 and DEB-1054040 to PBA.
